### 2016-04-22 ch03-lrm/lrm-paper.tex
Extract MC figures
Actually include MC figures

\begin{itemize}
    \item \TODO{choice $s$ or $z$}
    \item \TODO{derivation Bias}
      \begin{itemize}
        \item \TODO{Good LPM window}
        \item \TODO{Good LRM window}
      \end{itemize}
    \item \TODO{influence of noise filter: mismatch with model}
\end{itemize}

@@

@@

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.62\figurewidth}
  \TODOfig[ RMS, bias, std for $\SNR = \infty$]
  \caption[Comparison of local models for $\SNR = \infty$]{Local modeling of a discrete-time system results in a relative approximation error of $-100\unit{dB}$.}
  \label{fig:nparam:comparison:noiseless}
\end{figure}

@@

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.62\figurewidth}
  \TODOfig[ RMS, bias, std for $\SNR = 60\unit{dB}$]
  \caption[Comparison of local models for $\SNR = 60 \unit{dB}$]{The \gls{RMSE}, bias and variance of different local modeling methods is compared as a function of the number of points in the $3\unit{dB}$ bandwidth of the system. A relative approximation error of $-100 \unit{dB}$ is observed.}
  \label{fig:nparam:comparison:hiSNR}
\end{figure}

\paragraph{Poor signal-to-noise ratios}
\begin{figure}
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.62\figurewidth}
  \TODOfig[ RMS, bias, std for $\SNR = 20\unit{dB}$]
  \caption[Comparison of local models for $\SNR = 20 \unit{dB}$]{The \gls{RMSE}, bias and variance of different local modeling methods is compared as a function of the number of points in the $3\unit{dB}$ bandwidth of the system when $\SNR = 20\unit{dB}$. The \gls{LRM} outperforms the \gls{LPM}.}
  \label{fig:nparam:comparison:lowSNR}
\end{figure}

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.62\figurewidth}
  \TODOfig[ RMS, bias, std for $\SNR = 10\unit{dB}$]
  \caption[Comparison of local models for $\SNR = 10 \unit{dB}$]{The \gls{RMSE}, bias and variance of different local modeling methods is compared as a function of the number of points in the $3\unit{dB}$ bandwidth of the system when $\SNR = 20\unit{dB}$. An approximation error of $-100 \unit{dB}$ is observed.}
  \label{fig:nparam:comparison:terribleSNR}
\end{figure}

>>>>

\begin{itemize}
    \item \TODO{choice $s$ or $z$}
    \item \TODO{influence of noise filter: mismatch with model}
\end{itemize}

@@

\begin{table}
\centering
\caption{Local modeling methods used in the Monte Carlo analysis.}
\label{tbl:nparam:methods}
\begin{tabular}{lcccr} \toprule
\textsc{Method} & \DOF & $\nWind$ & $\nth$ & $\Delta$ SNR (dB)\\
\midrule
\color{rgb:red,196;green,160;blue,0} $\ETFE$ & 1 & 0  & 1 & 0 \\
\color{rgb:red,92;green,53;blue,102} $\lrm{7,1,1,1}$ & 15 & 10 & 5 & 4.77121 \\
\color{rgb:red,78;green,154;blue,6} $\lric{7,2,2,2}$ &  15&7 & 8 & 2.73001 \\
\color{rgb:red,32;green,74;blue,135} $\lrm{7,2,2,2}$ &  15&7 & 8 & 2.73001 \\
\color{rgb:red,206;green,92;blue,0} $\lrm{6,2,2,2}$ &  135 & 8 & 2.10853 \\
\color{rgb:red,164;green,0;blue,0} $\lpm{7,4,4}$ &  15&5 & 10 & 1.76091 \\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.62\figurewidth}
  \input{\thisDir/figs/MC-SNR-Inf.tikz}
  \caption[Comparison of local models for $\SNR = \infty$]{Local modeling of a discrete-time system results in an approximation error that is low enough for many practical uses.}
  \label{fig:nparam:comparison:noiseless}
\end{figure}

@@

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.62\figurewidth}
  \input{\thisDir/figs/MC-SNR-60.tikz}
  \caption[Comparison of local models for $\SNR = 60 \unit{dB}$]{The \gls{RMSE}, bias and variance of different local modeling methods is compared as a function of the number of points in the $3\unit{dB}$ bandwidth of the system. A relative approximation error of $-100 \unit{dB}$ is observed.}
  \label{fig:nparam:comparison:hiSNR}
\end{figure}

\paragraph{Poor signal-to-noise ratios}
\begin{figure}
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.62\figurewidth}
  \input{\thisDir/figs/MC-SNR-20.tikz}
  \caption[Comparison of local models for $\SNR = 20 \unit{dB}$]{The \gls{RMSE}, bias and variance of different local modeling methods is compared as a function of the number of points in the $3\unit{dB}$ bandwidth of the system when $\SNR = 20\unit{dB}$. The \gls{LRM} outperforms the \gls{LPM}.}
  \label{fig:nparam:comparison:lowSNR}
\end{figure}

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.62\figurewidth}
  \input{\thisDir/figs/MC-SNR-10.tikz}
  \caption[Comparison of local models for $\SNR = 10 \unit{dB}$]{The \gls{RMSE}, bias and variance of different local modeling methods is compared as a function of the number of points in the $3\unit{dB}$ bandwidth of the system when $\SNR = 20\unit{dB}$. An approximation error of $-100 \unit{dB}$ is observed.}
  \label{fig:nparam:comparison:terribleSNR}
\end{figure}
